\documentclass[margin, 10pt]{res} 
\usepackage{helvet}
\usepackage{framed}
\usepackage{tabstackengine}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{longtable}
\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!red,
  urlcolor=black!50!red
}
\setlength{\textwidth}{5.1in}

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Enrico Buratto, Curriculum Vitae}
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
\moveleft.5\hoffset\centerline{Via Tiziano Vecellio 3}
\moveleft.5\hoffset\centerline{31030 Dosson di Casier (TV), Italy}
\moveleft.5\hoffset\centerline{(+39) 346 832 2431}
\moveleft.5\hoffset\centerline{enrico.buratto.pub96@gmail.com}
\moveleft.5\hoffset\centerline{www.linkedin.com/in/enrico-buratto-04104b151}

\begin{resume}

%----------------------------------------------------------------------------------------
%	Technology SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Technology \\ skills} 

\textbf{Programming languages: } C++ \textit{(principal language)}, Java \textit{(basic level)}, Java for Android \textit{(basic level)}, Matlab \textit{(basic level)}, Ampl \textit{(basic level)}, C \textit{(basic level)}.

\textbf{Backend web languages: } PHP, SQL.

\textbf{Frontend web languages: } HTML5, XHTML 1.0, CSS 3, Javascript.

\textbf{Database design and management: } PhpMyAdmin, MySQL.

\textbf{Version Control Systems: } Git, Github.

\textbf{Operating Systems: } GNU/Linux \textit{(principal OS, particularly Arch Linux and Debian)}, Microsoft Windows, Apple macOS.

\textbf{Microsoft Office suite and Open Source alternatives.}

\textbf{\LaTeX}.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%---------------------------------------------------------------------------------------- 

\section{Education}
\textbf{Computer Science, BSc level} \hfill October 2016 - now \\
\textit{Università degli Studi di Padova, Italy} \\ \\
\textbf{Physics, BSc level} \hfill October 2015 - June 2016 \\
\textit{Università degli Studi di Padova, Italy} \\ \\
\textbf{Scientific High School} \hfill September 2010 - June 2015 \\
\textbf{"Scienze Applicate" option} \\
Final grade: 77/100 \\
\textit{Liceo Scientifico "Leonardo Da Vinci" - Treviso, Italy} 

\section{Course of \\ Study}
\begin{longtable}{lllll}
\textbf{Course Code} & \textbf{Name}                   & \textbf{Year} & \textbf{ECTS}     & \textbf{Final Grade} \\
SCP4063958            & Algebra and Discrete Mathematics   & 1             & 12               & 30                   \\
SCP4063959            & Mathematical Analysis              & 1             & 12               & 18                   \\
SC0112464             & Computer Architecture  & 1             & 8                & 25                   \\
SC02105452            & Logic                          & 1             & 6                & 21                   \\
SC02121720            & Programming                  & 1             & 10               & 26                   \\
SCP4063963            & Operative Systems               & 1             & 9                & 26                   \\
SCP4065531            & Algorithms and Data Structures      & 2             & 9                & 24                   \\
SC03100756            & Automata and Formal Languages      & 2             & 8                & 23                   \\
SCP4065533            & Database                    & 2             & 9                & 25                   \\
SCP4063208            & Numerical Analysis                & 2             & 7                & 30L                  \\
SC03106737            & Probability and Statistics        & 2             & 6                & 30L                  \\
SC01122887            & Computer Networks and Security                & 2             & 10               & 18                   \\
SCP4065562            & Operations Research               & 3             & 7                & 30L                  \\
SC01123013            & Open-Source Technologies           & 3             & 6                & 26                   \\
SCP4065581            & Web Technologies                  & 3             & 9                & 29                   \\
SCP6076298            & Web Information Management      & 3             & 6                & 27                   \\
\textbf{}             & \textbf{Total/Weighted Average} & \textbf{}     & \textbf{137/180} & \textbf{25.22/30}   
\end{longtable}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%---------------------------------------------------------------------------------------- 

\section{Training and\\ extracurricular \\ projects}
\textbf{Web Technologies project} \hfill November 2018 - February 2019 \\
Website designing and writing in HTML, CSS, PHP, JavaScript, SQL. GitHub repo \href{https://github.com/enricobu96/TecWebUNIPD}{here}.\\ \\
\textbf{Capture the Flag} \hfill January 2018 - April 2018 \\
Participation in a series of meetings focused on the computer security, held by the \href{https://github.com/enricobu96/TecWebUNIPD}{SPRITZ group}. \\
\textit{Università degli Studi di Padova} \\ \\
\textbf{Databases project} \hfill November 2017 - February 2018 \\
Group project consising of designing and implementation of a social network's database. GitHub repo \href{https://github.com/enricobu96/DB1718}{here}. \\ \\
\textbf{Participation in the Zero Robotics contest} \hfill 2013-2014 \\
Competition announced by "Ente Spaziale Europeo (ESA)" consisting of \href{https://www.esa.int/Science_Exploration/Human_and_Robotic_Exploration/Education/Robot_Spheres_in_zero-gravity_action}{Spheres}' programming.

%----------------------------------------------------------------------------------------
%	OBJECTIVES AND INTERESTS SECTION
%---------------------------------------------------------------------------------------- 

\section{Interests}
Developing of webpages and web applications both frontend side and backend side. \\
Explore Web phenomena such as people's approach to the Web and Semantic Web in general. \\
Computer security and reliable systems, with particular care for web security. \\
Computer networks design and implementation. \\
Imperative and Object-Oriented Programming. \\



%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{Working \\ Experience}

\textbf{Internet Ads Assessor} \hfill October 2019 - now \\
\textit{lionbridge.com} \\
Google Ads evaluation.

\textbf{Columnist} \hfill January 2016 - January 2019 \\
\textit{o2o.it}
\begin{itemize}
\item Writing of Computer Science-related articles;
\item Writing of generic articles.
\end{itemize} 


%----------------------------------------------------------------------------------------
%	COMMUNITY SERVICE SECTION
%---------------------------------------------------------------------------------------- 

\section{Volunteering}

\textbf{Scout Lead} \hfill February 2015 - now \\
\textit{AGESCI Gruppo Treviso 3} \\ \\
\textbf{Volunteer bartender} \hfill 2012 - now \\
\textit{"Fiera 4 Passi", Treviso} \\ \\
\textbf{Volunteering with homeless people} \hfill 2013 - 2014 \\
\textit{"Emergenza freddo", cooperative "La Esse Treviso"} \\ \\
\textbf{Volunteering with old people} \hfill September 2012 - June 2013 \\
\textit{Nursing Home "Casa Mia", Dosson di Casier (TV)} 


%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%---------------------------------------------------------------------------------------- 

\section{Languages}
\textbf{Italian: } Mother Tongue. \\
\textbf{English: } Good knowledge, receptive B2 certification.

\end{resume}
\end{document}